Refinements for open automata

### 2022-02-14 2021-Refinement/paper/refinementarticle.tex
part...

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By building  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
We have also:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
As $t_{13}$ and $t_{23}$ are built with the same transitions of $A_3$  (up renaming) so we can deduce:
\begin{align*}
{\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} & \Rightarrow  {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3} \beta_{13j} = \beta_{23xj}}\\
& \Rightarrow {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}}\\
\end{align*}
On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
In addition as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

@@

By adding the same (and equivalent) terms  to both sides of the implication of the formula $(*)$,  and  from all the implications induced by the extension of the valuation context mentioned above, we get:
\begin{multline*}
V_1 \uplus V_2 \uplus \fvars{t_1} \uplus V^1_3  \uplus V^2_3 \vdash\\
R\mpar{s_1, s_{2}} \wedge g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} %\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j}\! =\! \beta_{23xj}\\
			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
		\end{array}}   
\end{multline*}

>>>>

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By building  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
We have also:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
So we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up  renaming) hence we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\

Assuming we have $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ then we can deduce:
\begin{align*}
& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_1}\vdash  {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow &  V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
\end{align*}
On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
In addition as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

@@

From all the implications induced by the extension of the valuation context mentioned above, and by entering   all previous intermediate results in the formula $(*)$, we get:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_1} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} %\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
		\end{array}}   
\end{multline*}
